Formula translation in \changed{Blitz++, NumPy} and modern Fortran: a~case~study~of~the~language~choice tradeoffs

### 2014-02-19 paper/doc/code-for-listings.f.tex
the new order
changes before Sci Prog resubmission

    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{length} \PY{o}{=} \PY{n+nv}{n}
    \PY{k}{allocate}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{at}\PY{p}{(} \PY{o}{-}\PY{n+nv}{n} \PY{p}{:} \PY{n+nv}{n}\PY{o}{-}\PY{l+m+mi}{1} \PY{p}{)}\PY{p}{)}
    \PY{k}{allocate}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{arrs}\PY{p}{(} \PY{l+m+mi}{0} \PY{p}{:} \PY{n+nv}{n}\PY{o}{-}\PY{l+m+mi}{1} \PY{p}{)}\PY{p}{)}
  \PY{k}{end }\PY{k}{subroutine}

@@

    \PY{k}{allocate}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{arrs}\PY{p}{(}\PY{n+nv}{n}\PY{p}{)}\PY{p}{\PYZpc{}}\PY{n+nv}{a}\PY{p}{(} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{p}{)}\PY{p}{)}
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{at}\PY{p}{(}\PY{n+nv}{n}\PY{p}{)}\PY{p}{\PYZpc{}}\PY{n+nv}{p} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{arrs}\PY{p}{(}\PY{n+nv}{n}\PY{p}{)}
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{at}\PY{p}{(}\PY{n+nv}{n} \PY{o}{-} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{length}\PY{p}{)}\PY{p}{\PYZpc{}}\PY{n+nv}{p} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{arrs}\PY{p}{(}\PY{n+nv}{n}\PY{p}{)}
  \PY{k}{end }\PY{k}{subroutine}
\PY{k}{end }\PY{k}{module}
\PY{c}{!listing03}
\PY{k}{module }\PY{n+nv}{arakawa\PYZus{}c\PYZus{}m}
  \PY{k}{implicit }\PY{k}{none}

@@

\PY{k}{  }\PY{k}{interface }\PY{n+nv}{operator} \PY{p}{(}\PY{o}{-}\PY{p}{)}
    \PY{k}{module }\PY{n+nv}{procedure} \PY{n+nv}{mh}
  \PY{k}{end }\PY{k}{interface}

@@

\PY{k}{  }\PY{k}{elemental }\PY{k}{function }\PY{n+nv}{mh}\PY{p}{(}\PY{n+nv}{i}\PY{p}{,} \PY{n+nv}{h}\PY{p}{)} \PY{k}{result} \PY{p}{(}\PY{k}{return}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{i} 
    \PY{k}{type}\PY{p}{(}\PY{n+nv}{half\PYZus{}t}\PY{p}{)}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{h}
    \PY{k+kt}{integer} \PY{k+kd}{::} \PY{k}{return}
\PY{k}{    }\PY{k}{return} \PY{o}{=} \PY{n+nv}{i} \PY{o}{-} \PY{l+m+mi}{1}
  \PY{k}{end }\PY{k}{function}
\PY{k}{end }\PY{k}{module}
\PY{c}{!listing04}
\PY{k}{module }\PY{n+nv}{halo\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{arakawa\PYZus{}c\PYZus{}m}
  \PY{k}{implicit }\PY{k}{none}

    \PY{k}{return} \PY{o}{=} \PY{p}{(}\PY{o}{/} \PY{n+nv}{r}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{o}{-} \PY{n+nv}{n}\PY{p}{,} \PY{n+nv}{r}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{o}{+} \PY{n+nv}{n} \PY{o}{/}\PY{p}{)}
  \PY{k}{end }\PY{k}{function}

    \PY{k}{return} \PY{o}{=} \PY{p}{(}\PY{o}{/} \PY{n+nv}{r}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{o}{-} \PY{n+nv}{h}\PY{p}{,} \PY{n+nv}{r}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{o}{+} \PY{n+nv}{h} \PY{o}{/}\PY{p}{)}
  \PY{k}{end }\PY{k}{function}
\PY{k}{end }\PY{k}{module}
\PY{c}{!listing05}
\PY{k}{module }\PY{n+nv}{pi\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{real\PYZus{}m}
  \PY{k}{implicit }\PY{k}{none}
\PY{k}{  }\PY{k}{contains}
\PY{k}{  }\PY{k}{function }\PY{n+nv}{pi}\PY{p}{(}\PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{arr}\PY{p}{,} \PY{n+nv}{i}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)} \PY{k}{result}\PY{p}{(}\PY{k}{return}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{d}
    \PY{k+kt}{real}\PY{p}{(}\PY{n+nv}{real\PYZus{}t}\PY{p}{)}\PY{p}{,} \PY{k}{allocatable}\PY{p}{,} \PY{k}{target} \PY{k+kd}{::} \PY{n+nv}{arr}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{)}
    \PY{k+kt}{real}\PY{p}{(}\PY{n+nv}{real\PYZus{}t}\PY{p}{)}\PY{p}{,} \PY{k}{pointer} \PY{k+kd}{::} \PY{k}{return}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}
    \PY{k}{select }\PY{k}{case} \PY{p}{(}\PY{n+nv}{d}\PY{p}{)} 
      \PY{k}{case} \PY{p}{(}\PY{l+m+mi}{0}\PY{p}{)} 
        \PY{k}{return} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{arr}\PY{p}{(} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{p}{)}   
      \PY{k}{case} \PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} 
        \PY{k}{return} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{arr}\PY{p}{(} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{p}{)}   
    \PY{k}{end }\PY{k}{select}
\PY{k}{  }\PY{k}{end }\PY{k}{function}

\PY{k}{  }\PY{k}{pure }\PY{k}{function }\PY{n+nv}{span}\PY{p}{(}\PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{i}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)} \PY{k}{result}\PY{p}{(}\PY{k}{return}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{d}
    \PY{k+kt}{integer} \PY{k+kd}{::} \PY{k}{return}
\PY{k}{    }\PY{k}{select }\PY{k}{case} \PY{p}{(}\PY{n+nv}{d}\PY{p}{)}
      \PY{k}{case} \PY{p}{(}\PY{l+m+mi}{0}\PY{p}{)}
        \PY{k}{return} \PY{o}{=} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{o}{-} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1}
      \PY{k}{case} \PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)}
        \PY{k}{return} \PY{o}{=} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{o}{-} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1}
    \PY{k}{end }\PY{k}{select}
\PY{k}{  }\PY{k}{end }\PY{k}{function}
\PY{k}{end }\PY{k}{module}
\PY{c}{!listing06}
\PY{k}{module }\PY{n+nv}{bcd\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{arrvec\PYZus{}m}
  \PY{k}{implicit }\PY{k}{none}

\PY{k}{    }\PY{k}{subroutine }\PY{n+nv}{bcd\PYZus{}init}\PY{p}{(}\PY{n+nv}{this}\PY{p}{,} \PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{n}\PY{p}{,} \PY{n+nv}{hlo}\PY{p}{)}
      \PY{k}{import} \PY{k+kd}{::} \PY{n+nv}{bcd\PYZus{}t}
      \PY{k}{class}\PY{p}{(}\PY{n+nv}{bcd\PYZus{}t}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{this}
      \PY{k+kt}{integer} \PY{k+kd}{::} \PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{n}\PY{p}{,} \PY{n+nv}{hlo}
    \PY{k}{end }\PY{k}{subroutine}
\PY{k}{  }\PY{k}{end }\PY{k}{interface}
\PY{k}{end }\PY{k}{module}
\PY{c}{!listing07}
\PY{k}{module }\PY{n+nv}{solver\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{arrvec\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{bcd\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{arakawa\PYZus{}c\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{halo\PYZus{}m}
  \PY{k}{implicit }\PY{k}{none}

    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{i} \PY{o}{=} \PY{p}{(}\PY{o}{/} \PY{l+m+mi}{0}\PY{p}{,} \PY{n+nv}{nx} \PY{o}{-} \PY{l+m+mi}{1} \PY{o}{/}\PY{p}{)}
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{j} \PY{o}{=} \PY{p}{(}\PY{o}{/} \PY{l+m+mi}{0}\PY{p}{,} \PY{n+nv}{ny} \PY{o}{-} \PY{l+m+mi}{1} \PY{o}{/}\PY{p}{)}

\PY{k}{  }\PY{k}{subroutine }\PY{n+nv}{solver\PYZus{}cycle}\PY{p}{(}\PY{n+nv}{this}\PY{p}{)}
    \PY{k}{class}\PY{p}{(}\PY{n+nv}{solver\PYZus{}t}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{this}
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{n} \PY{o}{=} \PY{n+nb}{mod}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{n} \PY{o}{+} \PY{l+m+mi}{1} \PY{o}{+} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)} \PY{o}{-} \PY{l+m+mi}{2}
  \PY{k}{end }\PY{k}{subroutine}

    \PY{k}{do }\PY{n+nv}{t} \PY{o}{=} \PY{l+m+mi}{0}\PY{p}{,} \PY{n+nv}{nt}\PY{o}{-}\PY{l+m+mi}{1} 
      \PY{k}{call }\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{bcx}\PY{p}{\PYZpc{}}\PY{n+nv}{fill\PYZus{}halos}\PY{p}{(}                        \PY{p}{\PYZam{}}
        \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{psi}\PY{p}{\PYZpc{}}\PY{n+nv}{at}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{n}\PY{p}{)}\PY{p}{\PYZpc{}}\PY{n+nv}{p}\PY{p}{\PYZpc{}}\PY{n+nv}{a}\PY{p}{,} \PY{n+nv}{ext}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{j}\PY{p}{,} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{hlo}\PY{p}{)} \PY{p}{\PYZam{}}
      \PY{p}{)}
      \PY{k}{call }\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{bcy}\PY{p}{\PYZpc{}}\PY{n+nv}{fill\PYZus{}halos}\PY{p}{(}                        \PY{p}{\PYZam{}}
        \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{psi}\PY{p}{\PYZpc{}}\PY{n+nv}{at}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{n}\PY{p}{)}\PY{p}{\PYZpc{}}\PY{n+nv}{p}\PY{p}{\PYZpc{}}\PY{n+nv}{a}\PY{p}{,} \PY{n+nv}{ext}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{i}\PY{p}{,} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{hlo}\PY{p}{)} \PY{p}{\PYZam{}}
      \PY{p}{)}
      \PY{k}{call }\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{advop}\PY{p}{(}\PY{p}{)}
      \PY{k}{call }\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{k}{cycle}\PY{p}{(}\PY{p}{)}
    \PY{k}{end }\PY{k}{do}
\PY{k}{  }\PY{k}{end }\PY{k}{subroutine}
\PY{k}{end }\PY{k}{module}
\PY{c}{!listing08}
\PY{k}{module }\PY{n+nv}{cyclic\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{bcd\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{pi\PYZus{}m}
  \PY{k}{implicit }\PY{k}{none}
\PY{k}{  }
\PY{k}{  }\PY{k}{type}\PY{p}{,} \PY{n+nv}{extends}\PY{p}{(}\PY{n+nv}{bcd\PYZus{}t}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{cyclic\PYZus{}t}
    \PY{k+kt}{integer} \PY{k+kd}{::} \PY{n+nv}{d}
    \PY{k+kt}{integer} \PY{k+kd}{::} \PY{n+nv}{left\PYZus{}halo}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{rght\PYZus{}halo}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} 
    \PY{k+kt}{integer} \PY{k+kd}{::} \PY{n+nv}{left\PYZus{}edge}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{rght\PYZus{}edge}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} 
    \PY{k}{contains}
\PY{k}{    }\PY{n+nv}{procedure} \PY{k+kd}{::} \PY{n+nv}{init} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{cyclic\PYZus{}init}
    \PY{n+nv}{procedure} \PY{k+kd}{::} \PY{n+nv}{fill\PYZus{}halos} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{cyclic\PYZus{}fill\PYZus{}halos}
  \PY{k}{end }\PY{k}{type}

    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{d} \PY{o}{=} \PY{n+nv}{d}
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{left\PYZus{}halo} \PY{o}{=} \PY{p}{(}\PY{o}{/} \PY{o}{-}\PY{n+nv}{hlo}\PY{p}{,} \PY{o}{-}\PY{l+m+mi}{1} \PY{o}{/}\PY{p}{)} 
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{rght\PYZus{}halo} \PY{o}{=} \PY{p}{(}\PY{o}{/} \PY{n+nv}{n}\PY{p}{,} \PY{n+nv}{n}\PY{o}{-}\PY{l+m+mi}{1}\PY{o}{+}\PY{n+nv}{hlo} \PY{o}{/}\PY{p}{)} 
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{left\PYZus{}edge} \PY{o}{=} \PY{p}{(}\PY{o}{/} \PY{l+m+mi}{0}\PY{p}{,} \PY{n+nv}{hlo}\PY{o}{-}\PY{l+m+mi}{1} \PY{o}{/}\PY{p}{)}
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{rght\PYZus{}edge} \PY{o}{=} \PY{p}{(}\PY{o}{/} \PY{n+nv}{n}\PY{o}{-}\PY{n+nv}{hlo}\PY{p}{,} \PY{n+nv}{n}\PY{o}{-}\PY{l+m+mi}{1} \PY{o}{/}\PY{p}{)}
  \PY{k}{end }\PY{k}{subroutine}

\PY{k}{  }\PY{k}{subroutine }\PY{n+nv}{cyclic\PYZus{}fill\PYZus{}halos}\PY{p}{(}\PY{n+nv}{this}\PY{p}{,} \PY{n+nv}{a}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)}
    \PY{k}{class}\PY{p}{(}\PY{n+nv}{cyclic\PYZus{}t}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{this}
    \PY{k+kt}{real}\PY{p}{(}\PY{n+nv}{real\PYZus{}t}\PY{p}{)}\PY{p}{,} \PY{k}{allocatable} \PY{k+kd}{::} \PY{n+nv}{a}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{)}
    \PY{k+kt}{integer} \PY{k+kd}{::} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}
    \PY{n+nv}{ptr} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{pi}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{a}\PY{p}{,} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{left\PYZus{}halo}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)} 
    \PY{n+nv}{ptr} \PY{o}{=}  \PY{n+nv}{pi}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{a}\PY{p}{,} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{rght\PYZus{}edge}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)}
    \PY{n+nv}{ptr} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{pi}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{a}\PY{p}{,} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{rght\PYZus{}halo}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)} 
    \PY{n+nv}{ptr} \PY{o}{=}  \PY{n+nv}{pi}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{a}\PY{p}{,} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{left\PYZus{}edge}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)}

@@

@@

@@

      \PY{p}{(}\PY{n+nv}{C} \PY{o}{-} \PY{n+nb}{abs}\PY{p}{(}\PY{n+nv}{C}\PY{p}{)}\PY{p}{)} \PY{o}{*} \PY{n+nv}{psi\PYZus{}r}                             \PY{p}{\PYZam{}}

@@

@@

@@

\PY{c}{!listing15}

@@

\PY{c}{!listing16}

@@

\PY{c}{!listing17}

>>>>

    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{length} \PY{o}{=} \PY{n+nv}{n}
    \PY{k}{allocate}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{at}\PY{p}{(} \PY{o}{\PYZhy{}}\PY{n+nv}{n} \PY{p}{:} \PY{n+nv}{n}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1} \PY{p}{)}\PY{p}{)}
    \PY{k}{allocate}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{arrs}\PY{p}{(} \PY{l+m+mi}{0} \PY{p}{:} \PY{n+nv}{n}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1} \PY{p}{)}\PY{p}{)}
  \PY{k}{end }\PY{k}{subroutine}

@@

    \PY{k}{allocate}\PY{p}{(}\PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{arrs}\PY{p}{(}\PY{n+nv}{n}\PY{p}{)}\PY{p}{\PYZpc{}}\PY{n+nv}{a}\PY{p}{(} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{p}{)}\PY{p}{)}
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{at}\PY{p}{(}\PY{n+nv}{n}\PY{p}{)}\PY{p}{\PYZpc{}}\PY{n+nv}{p} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{arrs}\PY{p}{(}\PY{n+nv}{n}\PY{p}{)}
    \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{at}\PY{p}{(}\PY{n+nv}{n} \PY{o}{\PYZhy{}} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{length}\PY{p}{)}\PY{p}{\PYZpc{}}\PY{n+nv}{p} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{this}\PY{p}{\PYZpc{}}\PY{n+nv}{arrs}\PY{p}{(}\PY{n+nv}{n}\PY{p}{)}
  \PY{k}{end }\PY{k}{subroutine}
\PY{k}{end }\PY{k}{module}
\PY{c}{!listing03}
\PY{k}{module }\PY{n+nv}{arakawa\PYZus{}c\PYZus{}m}
  \PY{k}{implicit }\PY{k}{none}

@@

\PY{k}{  }\PY{k}{interface }\PY{n+nv}{operator} \PY{p}{(}\PY{o}{\PYZhy{}}\PY{p}{)}
    \PY{k}{module }\PY{n+nv}{procedure} \PY{n+nv}{mh}
  \PY{k}{end }\PY{k}{interface}

@@

\PY{k}{  }\PY{k}{elemental }\PY{k}{function }\PY{n+nv}{mh}\PY{p}{(}\PY{n+nv}{i}\PY{p}{,} \PY{n+nv}{h}\PY{p}{)} \PY{k}{result} \PY{p}{(}\PY{k}{return}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{i} 
    \PY{k}{type}\PY{p}{(}\PY{n+nv}{half\PYZus{}t}\PY{p}{)}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{h}
    \PY{k+kt}{integer} \PY{k+kd}{::} \PY{k}{return}
\PY{k}{    }\PY{k}{return} \PY{o}{=} \PY{n+nv}{i} \PY{o}{\PYZhy{}} \PY{l+m+mi}{1}
  \PY{k}{end }\PY{k}{function}
\PY{k}{end }\PY{k}{module}
\PY{c}{!listing04}
\PY{k}{module }\PY{n+nv}{pi\PYZus{}m}
  \PY{k}{use }\PY{n+nv}{real\PYZus{}m}
  \PY{k}{implicit }\PY{k}{none}
\PY{k}{  }\PY{k}{contains}
\PY{k}{  }\PY{k}{function }\PY{n+nv}{pi}\PY{p}{(}\PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{arr}\PY{p}{,} \PY{n+nv}{i}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)} \PY{k}{result}\PY{p}{(}\PY{k}{return}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{d}
    \PY{k+kt}{real}\PY{p}{(}\PY{n+nv}{real\PYZus{}t}\PY{p}{)}\PY{p}{,} \PY{k}{allocatable}\PY{p}{,} \PY{k}{target} \PY{k+kd}{::} \PY{n+nv}{arr}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{)}
    \PY{k+kt}{real}\PY{p}{(}\PY{n+nv}{real\PYZus{}t}\PY{p}{)}\PY{p}{,} \PY{k}{pointer} \PY{k+kd}{::} \PY{k}{return}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}
    \PY{k}{select }\PY{k}{case} \PY{p}{(}\PY{n+nv}{d}\PY{p}{)} 
      \PY{k}{case} \PY{p}{(}\PY{l+m+mi}{0}\PY{p}{)} 
        \PY{k}{return} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{arr}\PY{p}{(} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{p}{)}   
      \PY{k}{case} \PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} 
        \PY{k}{return} \PY{o}{=}\PY{o}{\PYZgt{}} \PY{n+nv}{arr}\PY{p}{(} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{:} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{p}{)}   
    \PY{k}{end }\PY{k}{select}
\PY{k}{  }\PY{k}{end }\PY{k}{function}

\PY{k}{  }\PY{k}{pure }\PY{k}{function }\PY{n+nv}{span}\PY{p}{(}\PY{n+nv}{d}\PY{p}{,} \PY{n+nv}{i}\PY{p}{,} \PY{n+nv}{j}\PY{p}{)} \PY{k}{result}\PY{p}{(}\PY{k}{return}\PY{p}{)}
    \PY{k+kt}{integer}\PY{p}{,} \PY{k}{intent}\PY{p}{(}\PY{n+nv}{in}\PY{p}{)} \PY{k+kd}{::} \PY{n+nv}{d}
    \PY{k+kt}{integer} \PY{k+kd}{::} \PY{k}{return}
\PY{k}{    }\PY{k}{select }\PY{k}{case} \PY{p}{(}\PY{n+nv}{d}\PY{p}{)}
      \PY{k}{case} \PY{p}{(}\PY{l+m+mi}{0}\PY{p}{)}
        \PY{k}{return} \PY{o}{=} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n+nv}{i}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1}
      \PY{k}{case} \PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)}
        \PY{k}{return} \PY{o}{=} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{2}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n+nv}{j}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1}
    \PY{k}{end }\PY{k}{select}

@@

\PY{c}{!listing05}

@@

\PY{c}{!listing06}

@@

      \PY{p}{(}\PY{n+nv}{C} \PY{o}{\PYZhy{}} \PY{n+nb}{abs}\PY{p}{(}\PY{n+nv}{C}\PY{p}{)}\PY{p}{)} \PY{o}{*} \PY{n+nv}{psi\PYZus{}r}                             \PY{p}{\PYZam{}}

@@

\PY{c}{!listing07}

@@

\PY{c}{!listing08}

@@

@@

@@
